% choose language here
\documentclass[a4paper,twoside,12pt,czech]{ctuThesis2}
\usepackage[czech]{babel}

\author{Student Hardworking}
\supervisor{Supervisor Strict}{A very famous institution}

% Consultant and second consultant. Comment out to ommit.
\consultant{Consultant Consulting}{An even more famous group}
\secondConsultant{Consultant Second}{Not that famous group}

% Comment out secondary language title if language is english
\title{O zvířatech}
\secondTitle{About animals}

\university{Forest university}
\faculty{School of Deer}
\department{Department of domestication}

\city{Praha}
\year{2022}

\major{Domestication}

% choose one of them or rename by yourself
\type{Bachelor thesis}
% \type{Research project}
% \type{Master thesis}

\scanOfAssignment{specimen1.pdf}{specimen2.pdf}

% use second keywords for english translation, comment out if not needed
\keywords{chov, krmení}
\secondKeywords{husbandry, feeding}

% use second abstract for english translation, comment out if not needed
\abstract{
Pellentesque congue aliquet nulla quis vestibulum. Aenean vitae porttitor nunc. Praesent imperdiet erat eget justo dictum tempus. Proin pulvinar metus eget arcu elementum blandit. Duis et lacus id tellus blandit eleifend. Vestibulum eleifend molestie scelerisque. Pellentesque convallis ex sed ipsum faucibus, in fermentum nunc dignissim. Nullam eu eros non enim mattis porttitor. Nunc maximus, elit placerat elementum faucibus, eros nisi rhoncus leo, a porttitor nisl ligula ac libero. Integer fermentum eget dolor id tempus.
  A decent abstract.
}
\secondAbstract{Translation of the abstract}

% use e.g. 
% Prohlašuji, že jsem svou bakalářskou práci vypracoval samostatně a použil jsem pouze podklady (literaturu, projekty, SW atd.) uvedené v přiloženém seznamu.
% I hereby admit that this work is original and all used resources have been cited in bibliography. 
\proclamation{Some proclamation of originality}

% use e.g.
% Autor děkuje vedoucímu práce za cenné rady.
% The author is grateful to the supervisor for valuable  
\acknowledgement{
  Some acknowledgement
}

% style of page layout
\pagestyle{fancy}
\fancyfoot{}
\fancyhead[RO,LE]{\thepage}
\fancyhead[RE]{\nouppercase{\leftmark}}
\fancyhead[LO]{\nouppercase{\rightmark}}

\begin{document}

% frontmatter changes page numbers to roman etc
\frontmatter

\maketitle

\includeAssignment

\makeProclamation

\makeAcknowledgement

\makeAbstract

\makeTOC

% the text itself begins here
\include{addons/acronyms}

\listoffigures

% normal numbering by arabic numbers
\mainmatter

\stdindent
\stdskip

\include{chapters/uvod}
\include{chapters/neco}
\include{chapters/zaver}

\printbibliography[heading=bibintoc]

\newpage
\appendix

\include{addons/appendix}

\end{document}